---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Welcome to StatAid

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

`StatAid` is a free open-source software provided as an R package allowing clinicians and researchers to perform statistic analysis through an intuitive graphical interface. It has been developed with the R software, using the [Shiny package](https://shiny.rstudio.com/). [Golem](https://github.com/ThinkR-open/golem) has been used for package compilation and deployment.  

 The software guide the users through the steps of a good data analysis, including multiple features:
<ul><li> Exploratory data analysis: distribution, count, missing-values and outliers check  </li>
<li> Descriptive analysis, simple comparative analysis and publication ready 'table 1' output </li>
<li> Publication-ready graph customization  </li>
<li> Paired data analysis (case-control studies, repetead measures) </li>
<li> Univariate analysis and models for continuous and categorical outcome: Correlation, linear and logistic regression  </li>
<li> Univariate analysis and models for time-dependant outcome: Kaplan-Meier curves and cox regression </li>
<li> Multivariate analysis and models for continuous, categorical and time-dependant outcomes </li></ul>

# Getting started

## Online version 

StatAid has a ready-to-use online version available at [https://vincentalcazer.shinyapps.io/StatAid/](https://vincentalcazer.shinyapps.io/StatAid/).

## Local version

You can install the development version from [GitHub](https://github.com/VincentAlcazer/StatAid) else by cloning the repository or directly by downloading the package in R:

```{r Github install }

# install.packages("remotes")
#remotes::install_github("VincentAlcazer/StatAid")

#StatAid::run_app()
```


# Troubleshooting and contribution

All troubleshooting and contributions can be found on the [Github page.](https://github.com/VincentAlcazer/StatAid/issues)

## Bug report

If you encounter any problem with the software or find a bug, please report it on GitHub:

- Create a [new issue](https://github.com/VincentAlcazer/StatAid/issues) on the Github page
- Try to describe the problem/bug with reproductible steps

## Feature request

To ask for new feature implementation/current feature enhancemenet:

- Create a [new issue](https://github.com/VincentAlcazer/StatAid/issues) on the Github page
- Briefly describe the research question you want to answer and the type of data you have
- If possible: provide pictures of the graph you would like to make or references from the paper you saw the analysis in.

## Contribution proposal

Contributions to new features or code enhancement are welcomed by creating a new [pull request.](https://github.com/VincentAlcazer/StatAid/pulls)

