---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Welcome to StatAid

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

`StatAid` is a free open-source software provided as an R package allowing clinicians and researchers to perform statistic analysis through an intuitive graphical interface. It has been developed with the R software, using the [Shiny package](https://shiny.rstudio.com/). [Golem](https://github.com/ThinkR-open/golem) has been used for package compilation and deployment.  

 The software guide the users through the steps of a good data analysis, including multiple features:
<ul><li> Exploratory data analysis: distribution, count, missing-values and outliers check  </li>
<li> Descriptive analysis, simple comparative analysis and publication ready 'table 1' output </li>
<li> Publication-ready graph customization  </li>
<li> Paired data analysis (case-control studies, repetead measures) </li>
<li> Univariate analysis and models for continuous and categorical outcome: Correlation, linear and logistic regression  </li>
<li> Univariate analysis and models for time-dependant outcome: Kaplan-Meier curves and cox regression </li>
<li> Multivariate analysis and models for continuous, categorical and time-dependant outcomes </li></ul>

# Getting started

## Online version 

StatAid has a ready-to-use online version available at [https://vincentalcazer.shinyapps.io/StatAid/](https://vincentalcazer.shinyapps.io/StatAid/).

## Local version

You can install the development version from [GitHub](https://github.com/VincentAlcazer/StatAid) else by cloning the repository or directly by downloading the package in R:

```{r Github install }

# install.packages("remotes")
#remotes::install_github("VincentAlcazer/StatAid")

#run_app()
```


# Troubleshooting / contact

 To report a bug or request/suggest a new feature, please open [Github issue.](https://github.com/VincentAlcazer/StatAid/issues)
 You can also contact me by [mail.](mailto:vincent.alcazer@chu-lyon.fr)
